---
title: "p8105_hw1_zz3167.Rmd"
author: "Zhiyi Zhu"
date: "2023-09-18"
output: github_document
---

## Problem 1

#### Load the package

```{r, echo=TRUE, message=FALSE}
library(moderndive)
library(tidyverse)
```

#### Load the `early_january_weather` dataset

```{r}
data("early_january_weather")
```

#### Description of the "early_january_weather" dataset

Below we describe the dataset including names / values of important variables, the size of the dataset, and the mean temperature:


* The variable names of the early_january_weather dataset are `r names(early_january_weather)`.

* There are `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables in this dataset. 

* The means temperature is `r round(mean(early_january_weather$temp, na.rm = TRUE),2)`.

#### Make a scatterplot of `temp` (y) vs `time_hour` (x)

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, colour = humid)) + geom_point() + labs(x = 'Time (h)', y = 'Temperature (F)', title = 'Scatter Plot of Temperature and Humidity')
```

#### Describe the patterns that are apparent in this plot

* Overall, with the increase of time, the temperature shows an increasing trend.
* Specific to a single day, the temperature is highest at noon and lowest at night.
* Specific to a single day, humidity decreases as the temperature rises.

#### Export the scatterplot to the project directory using ggsave

```{r, message=FALSE}
ggsave("time_temp_scatter.png")
```


## Problem 2

#### Create a data frame 

The data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
random_sample = rnorm(10)
vec_logical = random_sample > 0
vec_character =  c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
vec_factor = factor(rep(c("Excellent", "Good", "Pass"), length.out = 10))

Prob2_data = data.frame(RS = random_sample,
                        Logical = vec_logical,
                        Character = vec_character,
                        Factor = vec_factor)
print(Prob2_data)
```

#### Calculate the mean of each variable

The mean of the `random_sample` is `r mean(pull(Prob2_data, RS))`.  
The mean of the `vec_logical` is `r mean(pull(Prob2_data, Logical))`.  
The mean of the `vec_character` is `r mean(pull(Prob2_data, Character))`.  
The mean of the `vec_factor` is `r mean(pull(Prob2_data, Factor))`.

According to the result, We can calculate the mean of `random_sample` and `vec_logical`, but the mean of `vec_character` and `vec_factor` cannot be calculated.

#### Convert variables to another types

Below we convert logical, character and factor variables to numeric.

```{r,eval = FALSE}
num_logical = as.numeric(pull(Prob2_data, Logical))
num_character = as.numeric(pull(Prob2_data, Character))
num_factor = as.numeric(pull(Prob2_data, Factor))
```

#### Explain the phenomenon

We can find that using `as.numeric` function we could convert logical vectors and factor vectors to numeric vectors, but it does not work for character vectors.

Here is the explanation:

* **Logical values:** Logical values can be converted to numeric values by using `as.numeric` function. **`TRUE`** is converted to 1, and **`FALSE`** is converted to 0. So, when calculating the mean of a logical variable, R will treat **`TRUE`** as 1 and **`FALSE`** as 0 automatically, and the result will be a number.

* **Character values:** When applying `as.numeric` function to a character vector, whether or not the character vector can be converted to a numeric vector depends on the content of the character vector. If the characters are numeric (e.g., "10", "20", "30"), they will be successfully converted to numeric values (10, 20, 30). However, if the characters contain non-numeric characters (e.g., "A","B","C"), we will get NA values for those.

* **Factor values:** When applying `as.numeric` function to a factor vector, the factor will be first converted to it underlying integer code, and then the integer code is converted to numeric value. In R, we cannot calculate the mean of a factor vector directly because factors are categorical variables, and their values represent distinct categories or levels, but do not represent meaningful numeric values, so the mean is NA.


