---
title: "p8105_hw1_zz3167.Rmd"
author: "Zhiyi Zhu"
date: "2023-09-18"
output: github_document
---

## Problem 1

#### Load the package

```{r, echo=TRUE, message=FALSE}
library(moderndive)
library(tidyverse)
```

#### Load the `early_january_weather` dataset

```{r}
data("early_january_weather")
```

#### Description of the "early_january_weather" dataset

Below we describe the dataset including names / values of important variables, the size of the dataset, and the mean temperature:


* The variable names of the early_january_weather dataset are `r names(early_january_weather)`.

* There are `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables in this dataset. 

* The means temperature is `r round(mean(early_january_weather$temp, na.rm = TRUE),2)`.

#### Make a scatterplot of `temp` (y) vs `time_hour` (x)

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, colour = humid)) + geom_point() + labs(x = 'Time (h)', y = 'Temperature (F)', title = 'Scatter Plot of Temperature and Humidity')
```

#### Describe the patterns that are apparent in this plot

* Overall, with the increase of time, the temperature shows an increasing trend.
* Specific to a single day, the temperature is highest at noon and lowest at night.
* Specific to a single day, humidity decreases as the temperature rises.

#### Export the scatterplot to the project directory using ggsave

```{r, message=FALSE}
ggsave("time_temp_scatter.png")
```





