---
title: "p8105_hw1_zz3167.Rmd"
author: "Zhiyi Zhu"
date: "2023-09-18"
output: github_document
---

## Problem 1

#### Load the package

```{r, echo=TRUE, message=FALSE}
library(moderndive)
library(tidyverse)
```

#### Load the `early_january_weather` dataset

```{r}
data("early_january_weather")
```

#### Description of the "early_january_weather" dataset

Below we describe the dataset including names / values of important variables, the size of the dataset, and the mean temperature:


* The variable names of the early_january_weather dataset are `r names(early_january_weather)`.

* There are `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables in this dataset. 

* The means temperature is `r round(mean(early_january_weather$temp, na.rm = TRUE),2)`.

#### Make a scatterplot of `temp` (y) vs `time_hour` (x)

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, colour = humid)) + geom_point() + labs(x = 'Time (h)', y = 'Temperature (F)', title = 'Scatter Plot of Temperature and Humidity')
```

#### Describe the patterns that are apparent in this plot

* Overall, with the increase of time, the temperature shows an increasing trend.
* Specific to a single day, the temperature is highest at noon and lowest at night.
* Specific to a single day, humidity decreases as the temperature rises.

#### Export the scatterplot to the project directory using ggsave

```{r, message=FALSE}
ggsave("time_temp_scatter.png")
```


## Problem 2

#### Create a data frame 

The data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
random_sample = rnorm(10)
vec_logical = random_sample > 0
vec_character =  c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
vec_factor = factor(rep(c("Excellent", "Good", "Pass"), length.out = 10))

Prob2_data = data.frame(RS = random_sample,
                        Logical = vec_logical,
                        Character = vec_character,
                        Factor = vec_factor
                        )
print(Prob2_data)
```

#### Calculate the mean of each variable

The mean of the `random_sample` is `r mean(pull(Prob2_data, RS))`.  
The mean of the `vec_logical` is `r mean(pull(Prob2_data, Logical))`.  
The mean of the `vec_character` is `r mean(pull(Prob2_data, Character))`.  
The mean of the `vec_factor` is `r mean(pull(Prob2_data, Factor))`.

According to the result, We can calculate the mean of `random_sample` and `vec_logical`, but the mean of `vec_character` and `vec_factor` cannot be calculated.

#### Convert variables to another types

Below we convert logical, character, and factor variables to numeric

```{r}
num_logical = as.numeric(pull(Prob2_data, Logical))
num_character = as.numeric(pull(Prob2_data, Character))
num_factor = as.numeric(pull(Prob2_data, Factor))
```


